An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-01-13 preprint/manuscript.tex
minor tweaks

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
However, when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately there are good reasons to believe that the psychology literature is not a faithful representation of all research psychologists conduct.
For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in psychology:
Studying 362 empirical articles published in four psychology journals in 1955/56, Sterling (1959) found that a whopping \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in psychology reported support for their first or main hypothesis, the highest number of all disciplines in the study.
For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes must consistently be very high (given the same study design).

@@

Sterling (1959) already suspected a selection process behind the numbers he found:
\enquote{(\ldots{}) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Mahoney, 1977; Greenwald, 1975) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, n.d.).
These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).

Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because because it weeds out low-quality research that would only pollute the literature (Winter \& Happee, 2013; but see van Assen, van Aert, Nuijten, \& Wicherts, 2014).
How problematic selective publishing is in practice remains an empirical question:
If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results would contain a similar proportion of positive results as the current one.
But how many positive results would such an unbiased literature contain in reality?
We set out to explore this question by comparing the rate of positive results in a sample from the current psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.

@@

An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of p-hacking via restricted flexibility in data analysis.
However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias.
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
Registered Reports (RRs) are a new publication format with a restructured submission timeline:
Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline to a journal.
The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
The authors then collect and analyse the data and write up the final report.
The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
RRs thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 207 journals at the time of writing (\url{http://cos.io/rr}).

@@

Assuming a constant alpha level, the rate of positive results in a literature is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Szucs \& Ioannidis, 2017).
Therefore, if the emerging Registered Reports literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
At this time, we have good reasons to believe in a difference in bias, but little reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate (i.e., the proportion of supported hypotheses among all tested hypotheses).
Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.

@@

The goal of our study was to test if Registered Reports in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in psychology and compared them to all published Registered Reports in psychology.
Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
For standard reports we used the same sampling method (restricted to the psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
We chose Fanelli's method because Fanelli's (2010) and (2012) studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
We additionally coded if studies were replications or original work because many published Registered Reports are replications.
If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among Registered Reports than standard reports could therefore introduce a confound.

In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen and Mehler (2019) conducted a similar investigation:
They coded the proportion of null results in the 127 biomedical and psychology Registered Reports listed in the COS database as of September 2018.
We were not aware of their parallel efforts when we planned our study in September and October 2018.
Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
They compared these numbers to an estimate of \(5-20\%\) null results in the standard literature.
This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018){]}, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.

A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and provides an interesting resource for future meta-scientific research.

@@

After conducting a pilot to test the planned procedure we preregistered our study (\url{https://osf.io/s8e97}).
Methods and analyses described here were preregistered unless otherwise noted.
A detailed comparison of our preregistration and the eventual procedure is provided in the supplement.
We report how we determined our sample size, all data exclusions, and all measures in the study.

@@

We also wanted to code if a study was a replication of a previously published one:
We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study.
A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
Conceptual replications and internal replications were not counted as replications in this narrow sense:
The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(21.05 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

@@

It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems.
We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.

@@

We examined the proportion of psychology articles that find support for their first tested hypothesis and found a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.

The positive result rate we found in standard reports (\(96.05 \%\)) is slightly higher than the \(91.5\%\) reported by Fanelli (2010), although this difference was not statistically significant.
Our replication in a more recent sample of the psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf. Fanelli, 2012).
Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen and Mehler (2019), despite some differences in method and studied population.

@@

We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
Because neither hypotheses, authors, nor editors are randomly assigned to each publication format we cannot draw firm conclusions about the causes that lead to a difference in the proportion of supported hypotheses.
Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in psychology.
It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias.
Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use.
This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.

@@

\leavevmode\hypertarget{ref-Lakens2019b}{}%
Lakens, D. (n.d.). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}

>>>>

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
But when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that a whopping \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.

@@

Sterling (1959) already suspected a selection process behind the numbers he found:
\enquote{(\ldots{}) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, 2019).
These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).

Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature (Winter \& Happee, 2013; but see van Assen, van Aert, Nuijten, \& Wicherts, 2014).
How problematic selective publishing is in practice remains an empirical question:
If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results would contain a similar proportion of positive results as the current one.
But how many positive results would such an unbiased literature contain in reality?
We set out to explore this question by comparing the rate of positive results in a sample from the current Psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.

@@

An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias.
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
Registered Reports (RRs) are a new publication format with a restructured submission timeline:
Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline to a journal.
The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
The authors then collect and analyse the data and write up the final report.
The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (\url{http://cos.io/rr}).

@@

Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Szucs \& Ioannidis, 2017).
Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.

@@

The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology.
Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
We additionally coded if studies were replications or original work because many published Registered Reports are replications.
If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.

In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen and Mehler (2019) conducted a similar investigation:
They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018.
We were not aware of their parallel efforts when we planned our study in September and October 2018.
Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
They compared these numbers to an estimate of \(5-20\%\) null results in the standard literature.
This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018), who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.

A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.

@@

After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/s8e97}).
Methods and analyses described here were preregistered unless otherwise noted.
A detailed comparison of our preregistration and the eventual procedure is provided in the supplement.
We report how we determined our sample size, all data exclusions, and all measures in the study.

@@

We also wanted to code if a study was a replication of a previously published one:
We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study.
A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
After an initial coding attempt with ill-defined coding criteria led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
Conceptual replications and internal replications were not counted as replications in this narrow sense:
The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(21.05 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

@@

It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems.
We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.

@@

We examined the proportion of Psychology articles that find support for their first tested hypothesis and found a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.

The positive result rate we found in standard reports (\(96.05 \%\)) is slightly higher than the \(91.5\%\) reported by Fanelli (2010), although this difference was not statistically significant.
Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf. Fanelli, 2012).
Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen and Mehler (2019), despite some differences in method and studied population.

@@

We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
Because neither hypotheses, authors, nor editors were randomly assigned to each publication format we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology.
It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias.
Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use.
This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.

@@

\leavevmode\hypertarget{ref-Lakens2019b}{}%
Lakens, D. (2019). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}
